### 2016-11-04 JournalTorqueControl/theory.tex
Added the limit

First,  $l$ and $u$ for simplicity of the following derivations are defined for the uniform distribution. 
%defining torque uniform distribution
\begin{align}
l &= \max(0,\mu -\sqrt{3} \sigma) \, , u = \min({1,\mu+\sqrt{3}\sigma})
\end{align}
Therefore, the torque applied is:
\begin{align}
\tau_u &=  \frac{u^2-l^2}{4\sqrt{3}\sigma} \textrm{  for    }  u>l
\end{align}
To simplify derivations for triangular distribution we define bounds of integration as:
%define torque for triangular:
\begin{align}
l_1 &= \max({0,\mu-\sqrt{6}\sigma})\, , l_2 = \max({0,\mu})\\ \nonumber
u_1 &= \min({1,\mu})\, , u_2 = \min({1,\mu+\sqrt{6}\sigma}) \nonumber
\end{align}
Thus, torque is:
\begin{align}
\tau_t &= \frac{\tau_{left} + \tau_{right}}{36\sigma^2}
\end{align}
where $\tau_{left}$ and $\tau_{right}$ are defined as:
\begin{align}
\tau_{left} &=  {u_1}^2(2u_1 - 3\mu+3\sqrt{6}\sigma)\\ \nonumber
&-2{l_1}^3+3{l_1}^2(\mu-\sqrt{6}\sigma), & \textrm{for     } u_1 > l_1\\ \nonumber
\tau_{right} &= 2{l_2}^3-3{l_2}^2(\mu+\sqrt{6}\sigma)\\ \nonumber
&-{u_2}^2(2u_2 - 3\mu-3\sqrt{6}\sigma),  & \textrm{for     } u_2 > l_2\\ \nonumber
\end{align}
Torque by a uniformly distributed swarm is defined by:
%defining torque normal distribution
\begin{align} \nonumber
\tau_n &= \frac{\left(e^{\frac{\mu^2}{2\sigma^2}}-e^{\frac{(1-\mu)^2}{2\sigma^2}}\right)\sigma}{\sqrt{2\pi}}+ \frac{\mu}{2}\left(\erf\left(\frac{1-\mu}{\sqrt{2}\sigma}\right)+\erf\left(\frac{\mu}{\sqrt{2}\sigma}\right)\right) 
\end{align}

@@

%best place to push for normal distribution:
For all distributions, the $\mu$ that maximizes torque if $\sigma = 0$ is 1. For the $\tau_{pivot}$ case, the optimal $\mu$ moves in the $-x$ direction as $\sigma$ increases and approaches a limit. This limit is $\mu = 0$ for a uniformly distributed swarm and $\mu = \frac{\sqrt{2}}{2}$ for a triangularly distributed swarm as we can see from Eq.\ref{eq:triMaxTorque}. We used L'H\^opital's rule and found third derivative of the torque to find the limit when standard deviation goes to infinity. It was because in the first derivative numerator and denominator were both going to infinity and we were not able to calculate the limit. The result is:

\begin{align}
\lim_{\sigma\to\infty} \frac{d^3\tau_n}{d\mu}= \frac{3\mu}{2}-1
\end{align}

which means the best position to push the rod moves left until it reaches $\mu = \frac{2}{3}$.

>>>>

First,  $l$ and $u$ for simplicity of the following derivations are defined for the uniform distribution. 
%defining torque uniform distribution
\begin{align}
l &= \max(0,\mu -\sqrt{3} \sigma) \, , u = \min({1,\mu+\sqrt{3}\sigma})
\end{align}
Therefore, the torque applied is:
\begin{align}
\tau_u &=  \frac{u^2-l^2}{4\sqrt{3}\sigma} \textrm{  for    }  u>l
\end{align}
To simplify derivations for triangular distribution we define bounds of integration as:
%define torque for triangular:
\begin{align}
l_1 &= \max({0,\mu-\sqrt{6}\sigma})\, , l_2 = \max({0,\mu})\\ \nonumber
u_1 &= \min({1,\mu})\, , u_2 = \min({1,\mu+\sqrt{6}\sigma}) \nonumber
\end{align}
Thus, torque is:
\begin{align}
\tau_t &= \frac{\tau_{left} + \tau_{right}}{36\sigma^2}
\end{align}
where $\tau_{left}$ and $\tau_{right}$ are defined as:
\begin{align}
\tau_{left} &=  {u_1}^2(2u_1 - 3\mu+3\sqrt{6}\sigma)\\ \nonumber
&-2{l_1}^3+3{l_1}^2(\mu-\sqrt{6}\sigma), & \textrm{for     } u_1 > l_1\\ \nonumber
\tau_{right} &= 2{l_2}^3-3{l_2}^2(\mu+\sqrt{6}\sigma)\\ \nonumber
&-{u_2}^2(2u_2 - 3\mu-3\sqrt{6}\sigma),  & \textrm{for     } u_2 > l_2\\ \nonumber
\end{align}
Torque by a uniformly distributed swarm is defined by:
%defining torque normal distribution
\begin{align} \label{eq:normalTorque}
\tau_n &= \frac{\left(e^{\frac{\mu^2}{2\sigma^2}}-e^{\frac{(1-\mu)^2}{2\sigma^2}}\right)\sigma}{\sqrt{2\pi}}+ \frac{\mu}{2}\left(\erf\left(\frac{1-\mu}{\sqrt{2}\sigma}\right)+\erf\left(\frac{\mu}{\sqrt{2}\sigma}\right)\right) 
\end{align}

@@

%best place to push for normal distribution:
For all distributions, the $\mu$ that maximizes torque if $\sigma = 0$ is 1. For the $\tau_{pivot}$ case, the optimal $\mu$ moves in the $-x$ direction as $\sigma$ increases and approaches a limit. This limit is $\mu = 0$ for a uniformly distributed swarm and $\mu = \frac{\sqrt{2}}{2}$ for a triangularly distributed swarm as we can see from Eq.\ref{eq:triMaxTorque}. %We used L'H\^opital's rule and found third derivative of the torque to find the limit when standard deviation goes to infinity. It was because in the first derivative numerator and denominator were both going to infinity and we were not able to calculate the limit. The result is:
The first derivative of Eq.\ref{eq:normalTorque} is:
\begin{align}
\frac{d_{\tau}}{d_{\mu}}= \frac{1}{2}\left(\erf{\frac{1-\mu}{\sqrt{2}\sigma}}+ \erf{\frac{\mu}{\sqrt{2}\sigma}}\right)- \frac{e^{\frac{-(\mu-1)^2}{2\sigma^2}}}{\sqrt{2\pi}\sigma}
\end{align}

The limit as $\sigma\to\infty$ is $\frac{2 - 3 \mu}{\sigma^3 6 \sqrt{2 \pi}}$ which goes to zero as the swarm variance increases. However, the zero of the numerator is $\mu = \frac{2}{3}$ which means the best position to push the rod moves left until it reaches $\mu = \frac{2}{3}$.

%\begin{align}
%\lim_{\sigma\to\infty} \frac{d^3\tau_n}{d\mu}= \frac{3\mu}{2}-1
%\end{align}

%which means the best position to push the rod moves left until it reaches $\mu = \frac{2}{3}$.
